Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
Experiment strategy for implementing FF-Replan for MDP-FH and RDDLSim

\subsubsection{FF-Replan with Finite Horizon}

>>>>

\subsection{FF-Replan with Finite Horizon}

Gourmand already works with RDDLSim and MDPs with finite horizon. The original
FF-Replan is a Goal-Oriented MDP planner. For a Finite-Horizon each state at
the horizon is a goal. To compare Gourmand, that works with MDP-FH, with
FF-Replan, FF-Replan needs a slight update. It should not only execute FF for
one goal, but for all goals at the horizon. It could then start executing the
plan with the highest reward. Depending on the determinization method,
\emph{single-outcomes} or \emph{all-outcomes}, not all goals might be
reachable. Of course the performance decreases with an increase of goal states
at the horizon. A hash-table cache, as FF-Replan already uses can still be used
to store plans generated by FF from a state to goal states, however not only
the plan should be stored, but also the reward for this plan should be stored
to pick the plan with the highest expected reward.

Using the framework of Glutton and Gourmand, and the FF heuristic found in mGPT
\cite{bonet2011mgpt}, the updated FF-Replan can be implemented. The first step
of Gourmand is parsing the problem and creating a structure of the problem.
Instead of executing the Gourmand algorithm, this structure can be used to
determinize the problem by setting all probabilities of each action to 1
(\emph{all-outcome}) or all but one to 0 (\emph{single-outcome}). Using the
FF heuristic it can find plans for each goal and calculate the expected reward.
Then it can reuse the Gourmand framework to execute the plan by sending the
action to the RDDLSim server. Like FF-Replan if the server returns with a state
that is not in the plan the algorithm will replan. If a goal is reached it will
output the achieved reward.
